material and methods

### 2017-08-31 man/ms_1_material_methods.Rmd
update writing
update anovas methods

>>>>

We tested for significant differences between drought events (2005 and 2012) and oak population (northern and southern slopes) for each of the resilience indices. Robust two-way ANOVAs were used beacuse original and log-transformed data both did not match the assumptions of normality and homogeneity of variance [@Wilcox2012]. Robust measures of central tendency (M-estimator based on Huber's Psi) were used since they were close to mean value in all cases [@Wilcox2012]. When running the robust ANOVA test, data were boostrapped 3000 times and trimmed automatically to control the potential influence of outliers [@Field, @Wilcox2012]. Post-hoc differences were assessed pairwise using a similar boostrap test. All the robust ANOVA and post-hoc tests were carried out using the WRS2 [@Mair2017] and rcompanion [@Mangiafico2017] R packages. The level of significance was set at 0.05 and adjusted for multiple comparisons.
